01-deseq2-all

### 2019-03-14 scripts/00-datawrangling.Rmd
for realz rename

```{r write}
write.csv(colData_manipluation, "../results/00_colData_manipluation.csv", row.names = TRUE) 
write.csv(countData_manipluation, "../results/countData_manipluation.csv", row.names = TRUE) 
write.csv(colData_characterization, "../results/00_colData_characterization.csv", row.names = TRUE) 
write.csv(countData_characterization, "../results/00-countData-characterization.csv", row.names = TRUE) 
```

>>>>

```{r write}
write.csv(colData_manipluation, "../results/00_colData_manipluation.csv", row.names = TRUE) 
write.csv(countData_manipluation, "../results/00_countData_manipluation.csv", row.names = TRUE) 
write.csv(colData_characterization, "../results/00_colData_characterization.csv", row.names = TRUE) 
write.csv(countData_characterization, "../results/00_countData_characterization.csv", row.names = TRUE) 
```

### 2019-03-14 scripts/01-DESeq2-all.Rmd
for realz rename

summary(aov(PC1 ~ sex * treatment * tissue * treatment, data=pcadata)) 
summary(aov(PC2 ~ sex * treatment * tissue * treatment, data=pcadata))

>>>>

write.csv(pcadata, "../results/01_pcadata.csv")
write.csv(percentVar, "../results/01_percentVar.csv")

summary(aov(PC1 ~ sex * treatment * tissue * treatment, data=pcadata)) 
summary(aov(PC2 ~ sex * treatment * tissue * treatment, data=pcadata)) 
summary(aov(PC3 ~ sex * treatment * tissue * treatment, data=pcadata)) 
summary(aov(PC4 ~ sex * treatment * tissue * treatment, data=pcadata)) 
summary(aov(PC5 ~ sex * treatment * tissue * treatment, data=pcadata)) 
summary(aov(PC6 ~ sex * treatment * tissue * treatment, data=pcadata))
